Statistical performance analysis of data-driven neural mass models

### 2013-09-19 manuscript/manuscript.tex
Updated dynamic crb plot

>>>>

\subsection{Time}

Fig.~\ref{fig:DynamicCRB} displays the evolution of the Bayesian CRB for the first state of the model in \cite{Silva1974}. The solid line is for a relatively small prior covariance and low measurement noise; the dashed line is for a larger prior covariance and the dashed dotted line is for a large prior covariance and high measurement noise.

\begin{figure}[ht]
  \begin{center}
    \includegraphics{./figures/pdf/DynamicCRB}
  \end{center}
  \caption{The evolution of the BCRB for of the first state of model A. The ... }
  \label{fig:DynamicCRB}
\end{figure}
